---
title: "Lab 2"
authors: "Miranda Tilton, Gulzina Kuttubekova, Atousa Zarindast, Zhenzhen Chen"
date: "February 20, 2019"
output: html_document
---

Link to the repo:
```{r}
link <- "https://github.com/kgulzina/stat585lab2"
```



Libraries:
```{r, include = FALSE} 
library(ggplot2)
library(maps)
library(sf)
library(dplyr)
library(purrr)
library(ggspatial)
```



Fun with Middle Earth. We added labels for the cities using package: "ggspatial".
```{r, fig.width = 10, fig.height = 10}
# read the data set
cities <- read_sf("data/ME-GIS-master/Cities.shp")

# plot middle earth
p <- ggplot() +
  geom_sf(data = read_sf("data/ME-GIS-master/Coastline2.shp"), 
          colour="grey10", fill="grey90") +
  geom_sf(data = read_sf("data/ME-GIS-master/Rivers19.shp"), 
          colour="steelblue", size=0.3) +
  geom_sf(data = read_sf("data/ME-GIS-master/PrimaryRoads.shp"), 
          size = 0.7, colour="grey30") +
  geom_sf(data = read_sf("data/ME-GIS-master/Cities.shp")) +
  geom_sf_text(mapping = aes(label = Name), data = cities, na.rm = T) + 
  annotation_scale () + 
  annotation_north_arrow () +
  theme_bw()
p
```



Australia shapefile:
```{r}
ozbig <- read_sf("data/gadm36_AUS_shp/gadm36_AUS_1.shp")

oz_st <- maptools::thinnedSpatialPoly(
  as(ozbig, "Spatial"), tolerance = 0.1, 
  minarea = 0.001, topologyPreserve = TRUE)

oz <- st_as_sf(oz_st)
```

Some data exploration. Inner works: 
```{r}
# check if list
is.list(oz$geometry)

# check is double list
str(oz$geometry[[1]])

# see the matrix (any random)
head(oz$geometry[[11]][[1]][[1]])
```


The following functions read the data containing the coordinates into one dataframe and plot the resulting dataframe as a polygon. We have two functions, extract_data_L1() and extract_data_L2(), which are used according to the number of sub-lists in the geometry attribute of the list. Since the "oz" object has two lists nested for each object, we use the L2 function here.

```{r}
# This function extracts data from a shapefile with 1 level in spf$geometry
extract_data_L1 <- function(spf) {
# Reads in the shapefile and extracts data from nested lists, finally
# recording them into one data frame with columns: long, lat, group and
# order.
#
# Args:
#   spf:    shapefile of a country
#
# Output:
#   df:     data frame
    
    # all matrices will be concatenated to this df
    df <- data.frame(t(1:3))
    colnames(df) <- c("long", "lat", "group")
    
    # start group enumeration
    count = 1
    
    # use loops to read nested lists
    for (f in 1:length(spf$geometry)) {
        for (i in 1:length(spf$geometry[[f]])) {
            temp <- map_depth(spf$geometry[[f]][[i]], 1, .f = c(1))
            temp <- data.frame(matrix(unlist(temp), ncol = 2, byrow
                                      = FALSE))
            colnames(temp) <- c("long", "lat")
            temp$group <- rep(count, times = nrow(temp))
            df <- rbind(df, temp)
            count <- count + 1
        }
    }
    
    # remove first row
    df <- df[-1,]
    
    # add order variable
    df$order <- as.integer(1:nrow(df))
    return(df)
}

# This function extracts data from a shapefile with 2 levels in spf$geometry
extract_data_L2 <- function(spf) {
# Reads in the shapefile and extracts data from nested lists, finally
# recording them into one data frame with columns: long, lat, group and
# order.
#
# Args:
#   spf:    shapefile of a country
#
# Output:
#   df:     data frame
    
    # pull each first element from nested lists
    # remove hierarchy by flatten
    # map list with sublists to data.frame function
    # add new variable = "group"
    map_depth(.x = spf$geometry, 2, .f = c(1)) %>% flatten %>% 
        map_dfr(data.frame, .id = "group") -> df 
    
    # rename columns
    colnames(df) <- c("group", "long", "lat")
    
    # add new variable = "order"
    df$order <- seq(from = 1, to = nrow(df), by = 1)
    
    return(df)
}


ozplus <- extract_data_L2(oz)

# plot
ozplus %>% ggplot(aes(x = long, y = lat, group = group, na.rm = TRUE)) + geom_polygon(colour = "black", fill = "grey50")
```




GADM: is a service to provide boundaries without borders.

We chose Kyrgyzstan and downloaded the shapefile. The following code reads the shapefile and thins it, then extracts the data and plots the polygon. (Note: here, we're using the L2 function again, and the shapefule that has two nested lists.)

```{r}
# read data
kgbig <- read_sf("data/gadm36_KGZ_shp/gadm36_KGZ_2.shp")

kg_st <- maptools::thinnedSpatialPoly(
  as(kgbig, "Spatial"), tolerance = 0.1, 
  minarea = 0.001, topologyPreserve = TRUE)
kg <- st_as_sf(kg_st)

# trying the original function on this data, and it works
kgplus <- extract_data_L2(kg)

kgplus %>% ggplot(aes(x = long, y = lat, group = group, na.rm = TRUE)) + geom_polygon(colour = "black", fill = "grey50")
```

Here is the same code using a shapefile for Kyrgyzstan that is only nested one single time, and thus we use the L1 version of the function.

```{r}
# read data
kgbig <- read_sf("data/gadm36_KGZ_shp/gadm36_KGZ_1.shp")

kg_st <- maptools::thinnedSpatialPoly(
  as(kgbig, "Spatial"), tolerance = 0.1, 
  minarea = 0.001, topologyPreserve = TRUE)
kg <- st_as_sf(kg_st)

# trying the original function on this data, and it works
kgplus <- extract_data_L1(kg)

kgplus %>% ggplot(aes(x = long, y = lat, group = group, na.rm = TRUE)) + geom_polygon(colour = "black", fill = "grey50")
```

Pretty good plot. Resembles my country :D


We also include an example mapping Turkey using the L2 version of the function:

```{r}
turbig <- read_sf("data/gadm36_TUR_shp/gadm36_TUR_1.shp")

tur_st <- maptools::thinnedSpatialPoly(
  as(turbig, "Spatial"), tolerance = 0.1, 
  minarea = 0.001, topologyPreserve = TRUE)
tur <- st_as_sf(tur_st)

# trying the same function on this data
turplus <- extract_data_L2(tur)

turplus %>% ggplot(aes(x = long, y = lat, group = group, na.rm = TRUE)) + geom_polygon(colour = "black", fill = "grey50")
```